---
title: 'Generational Differences at Work: Pomp or Circumstance?'
author:
  - name: Renata Garcia Prieto Palacios Roji
    affil: 1
    orcid: '0000-0002-1099-3857'
  - name: Dr. Alicia Stachowski
    affil: 2
  - name: Dr. John Kulas
    affil: 1
affiliation:
  - num: 1
    address: Montclair State University
  - num: 2
    address: University of Wisonsin-Stout
column_numbers: 3
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoleft_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

Popular press, consultative white papers, and trade publications frequently highlight unique generational differences that are important to accommodate if organizations hope to achieve a wide range of valuable organizational outcomes (see, for example, the presentations of Forbes, 2018; PWC, 2011).

Becton and colleagues (2014) suggest that such perceptions of generational differences may be more strongly attributed to popular culture rather than proper social science, and that generational differences may be less influential on organizational behaviors than is suggested within the broader popular culture.

King et al. (2019) note that generational effects tend to be quite small, and this is supported via meta-analytic investigation of organizational outcomes across generations (Costanza et al., 2012).

A generational cohort is a group of people who are identified by birth year range (Ryder, 1965). In a meta-analysis on generational differences in work attitudes, Constanza et al. (2012) summarized the boundaries of cohort years for empirical studies. They suggest that even though names are generally agreed upon, the boundary definitions across investigations vary. For the purposes of this presentation we utilize the PEW research group;s categorization of generations (see Table1). 


## Objectives

The current paper seeks to extend our field’s understanding of the intergenerational workplace by approaching the question of generational differences from a novel angle – by documenting time spent on different categories of activities as indicated via purposeful random sampling. 


# Methods

Data from two publicly available archival sources were used. First, the Current Population Survey which is the federal government’s primary economic household survey. To capture this data, probability sampling of 60,000 households is done annually, and surveys are conducted in person or by phone regarding the prior week’s activities. The annual CPS is designed to represent the U.S. population ages 16+, and includes those not in the Armed Forces or institutions (e.g., prisons, nursing facilities).  

Second, data from the American Time Use Survey was also reviewed. The ATUS sample is a stratified random subset of those who completed the CPS, and surveys are conducted via phone. During the interview, respondents are asked to share how they spent their time from 4:00 a.m. to 4:00 p.m. the previous day. Thus, activity for the preceding 24 hours is captured. A conversational interviewing technique is used to allow the interviewers to guide respondents their day and request more detail as needed.

## Variables

*Generational Cohort* A generational cohort variable was created from two variables: respondent birthdate, and verification of their age in years.

*Time Working* Our operationalization of number of minutes worked collapsed time spent on the following activities together: “work, main job”, 2) “work, other job(s)”, 3) “security procedures related to work”, 4) “working, not elsewhere classified (n.e.c.)”, and 5) “work and work-related activities, n.e.c.”.

*Time Spent on Work-related Socializing* These included job-related activities, but would not be considered a formal part of one’s job-description (such as socializing, eating and drinking, performing security procedures, or exercising – all related to one’s work).

*Time Spent on other Income-generating Activities (Hobbying)* These include additional income-generating activities that would not be considered part of one’s main job or primary source of income. For example, time spent here would include engaging in hobbies, crafts, performances, providing services, and rental property activities that result in income.

*Time Spent Job-searching* This category included time spent on activities involving the process of job searching and applying to a job, such as interviewing, security procedures, waiting associated with the job search, and any other processes necessary to obtain a job. 


# Results



```{r mytable, out.width='80%'}
knitr::kable(iris[1:10, 1:4], caption = 'Table caption.',align = 'c',"html")
```

Or with figures: Figure \@ref(fig:standard-plot), or Figure \@ref(fig:morefigs).

```{r standard-plot, out.width='80%', fig.align='center', fig.cap='Great figure!', fig.height=5}
plot(mtcars[1:2])
```

```{r morefigs, out.width='80%', echo=TRUE, fig.cap='Amazing, right?!', fig.height=5}
data <- iris

plot(x = data$Sepal.Length, 
     y = data$Sepal.Width, 
     col = data$Species,
     pch = 19, 
     xlab = "Sepal Length (cm)",
     ylab = "Sepal Width (cm)")

```

# Next Steps

Aliquam sed faucibus risus, quis efficitur erat. Vestibulum semper mauris quis tempus eleifend. Aliquam sagittis dictum ipsum, quis viverra ligula eleifend ut. Curabitur sagittis vitae arcu eget faucibus. In non elementum felis. Duis et aliquam nunc. Nunc pulvinar sapien nunc, vel pretium nisi efficitur in. Fusce fringilla maximus leo et maximus. Fusce at ligula laoreet, iaculis mi at, auctor odio. Praesent sed elementum justo. Aenean consectetur risus rhoncus tincidunt efficitur. Praesent dictum mauris at diam maximus maximus [@R-posterdown].

# Conclusion

Try `posterdown` out! Hopefully you like it!

```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
